Pesticides pollution of small streams in Germany

### 2016-07-29 article.tex
added refs

where $No_i$ is the observed number of exceedances at site $i$, $Agri_i$ the proportion of agriculture within the catchment and $Size_i$ the catchment size of the site. 
We used the number of samplings ($n$) as an offset to account different sampling efforts. 
We modeled $No_i$ as resulting from a negative binomial distribution ($NB$).
$f_1$ and $f_2$ are smoothing functions using thin plate regression splines.
The degree of smoothness was estimated using restricted maximum likelihood \todo{cite and check wood 2011}.
Similar models were fitted to the number of EQS-exceedances and the 95th percentile of $log(TU_{max})$ (see Supplement for details).
GAM were fitted using the mgcv package \todo{citation mgcv}.

@@

\begin{figure}
  \includegraphics[width=\textwidth]{fig/figvar.pdf}
  \caption{Compound spectra of the different federal states. Left: Barcode plot - Each vertical line is an analysed compound. Right: MDS ordination. 
  Colors according to three groups determined by hierarchical clustering (see Supplement Figure (xxx).}
  \label{fig:figvar}
\end{figure}
\todo{prettify figure!}

@@

\begin{figure}
  \includegraphics[width=\textwidth]{fig/figrac.pdf}
  \caption{Effect of agriculture within the catchment (left) and catchment size (right) on the number of RAC exceedances. Red line marks statistically significant increases.
  }
  \label{fig:figrac}
\end{figure}

>>>>

where $No_i$ is the observed number of exceedances at site $i$, $Agri_i$ the proportion of agriculture within the catchment and $Size_i$ the catchment size of the site. 
We used the number of samplings ($n_i$) as an offset to account different sampling efforts. 
We modeled $No_i$ as resulting from a negative binomial distribution ($NB$).
$f_1$ and $f_2$ are smoothing functions using thin plate regression splines \citep{wood_thin_2003}.
The degree of smoothness was estimated using restricted maximum likelihood (REML) during model fitting process \citep{wood_fast_2011}.
Similar models were fitted to the number of EQS-exceedances and the 95th percentile of $log(TU_{max})$ (see Supplement for details).
GAM were fitted using the mgcv package \citep{wood_fast_2011}.

@@

\begin{figure}
  \includegraphics[width=\textwidth]{fig/figvar.pdf}
  \caption{Compound spectra of the different federal states. Left: Barcode plot - Each vertical line is an analysed compound. Right: MDS ordination. 
  Colors according to three groups determined by hierarchical clustering (see Supplement Figure xxx).}
  \label{fig:figvar}
\end{figure}
\todo{prettify figure!}

@@

\begin{figure}
  \includegraphics[width=0.8\textwidth]{fig/figrac.pdf}
  \caption{Effect of agriculture within the catchment (left) and catchment size (right) on the number of RAC exceedances. Red line marks statistically significant increases.
  }
  \label{fig:figrac}
\end{figure}
